### 2024-08-17 paper.tex
fix action, reason about fibers

Then, letting \(G_{wr}\) act on \(G\) by left multiplication, we obtain an action of \(G_{wr}\) on \(U_{wr} \times G\).

@@

    What kind?
    All I need is something that allows me to deduce the dimension of the quotient!

>>>>

Then, letting \(G_{wr}\) act on \(G\) by \(g \cdot h := hg^{-1}\), we obtain an action of \(G_{wr}\) on \(U_{wr} \times G\).

@@

    Let \(y \in V_{wr}\).
    By definition of \(V_{wr}\), there is \(P_y \in G\) with \(P_y \cdot y \in U_{wr}\).
    \[\varphi^{-1}(y) = \{(x, P) : P \cdot x = y = P_y^{-1} \cdot (P_y \cdot y)\} = \]
    \[\{(x, P) : x = (P^{-1} P_y^{-1}) \cdot (P_y \cdot y) \} = \]
    \[\{((P^{-1}P_y^{-1}) \cdot (P_y \cdot y), P) : (P^{-1} P_y^{-1}) \in G_{wr}\} = \] 
    \[(\textrm{taking } Q := P^{-1}P_y^{-1}, \textrm{ so } P = (QP_y)^{-1} = P_y^{-1} Q^{-1})\]
    \[\{(Q \cdot (P_y \cdot y), P_y^{-1} Q^{-1}) : Q \in G_{wr}\} = \]
    \[\{Q \cdot (P_y \cdot y, P_y^{-1}) : Q \in G_{wr}\}.\]
    So we see that the fibers are exactly the \(G_{wr}\)-orbits.
    \par Now, what kind of quotient is this?
    All I need is something that allows me to deduce the dimension of the quotient...
